On exponential sums arising from the classical doubling method

### 2025-03-03 paper.tex
Adding notations

\section{Notation}
Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter_{\finiteField} \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.

@@

Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$. Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$. Let $\fieldCharacter \colon \quadraticExtension \to \multiplicativegroup{\cComplex}$ be a non-trivial character.

>>>>

\section{Notation}
Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter_{\finiteField} \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character. Fix an algebraic closure $\algebraicClosure{\finiteField}$ of $\finiteField$. For any $k \ge 1$, let $\finiteFieldExtension{k} \slash \finiteField$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.

@@

Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$ contained in $\algebraicClosure{\finiteField}$. For any $k \ge 1$, let $\quadraticFieldExtension{k} \slash \quadraticExtension$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$. Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$. Let $\fieldCharacter \colon \quadraticExtension \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
